Effect of temporal sampling

### 2019-10-25 R/temporal-sampling.Rmd
knit rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = FALSE, warning = FALSE, message = FALSE)

@@

# Libraries
library(dplyr)
require(rioja)
require(vegan)
require(ade4)
require(changepoint)
require(ggplot2)
require(gridExtra)
require(plotly)
library(reshape)
```

@@

```{r strat plot zurich selected sp, include=T, echo=F}
if(is.zh){
  par(mfrow=c(1,1))
par(mar=c(5.1,4.1,2.1,20))
clado.clust<-strat.plot(cbind(zh[,colnames(zh) %in% c("LK","SC","DL","EL","EC","BL","BYL")], rowSums(zh[,-1][,!colnames(zh) %in% c("LK","SC","DL","EL","EC","BL","BYL")])),yvar=zh[,1],col.line="black",lwd.line=0,col.bar="black",lwd.bar=2, x.names=c(colnames(zh[colnames(zh) %in% c("LK","SC","DL","EL","EC","BL","BYL")]), "others"), cex.xlabel=1, srt.xlabel=30,scale.minmax=FALSE, y.rev = F,clust=clust)
addClustZone(clado.clust,clust,4,col="black")
}
```
<br>`r fig_cap("strat plot zurich selected sp", "Stratigraphic abundance of dominant cladoceran remains in Lake Zürich sediment core ZH17-21. Abbreviations: BL= Bosmina longirostris, EC= Eubosmina coregoni, EL= Eubosmina longispina, DL= Daphnia spp., LK= Leptodora kindti, BYL= Bythotrephes longismanus, SC= Sida crystallina")`

@@

```{r}
p1 <- ggplot(output, aes(Number_samples, PC1_var)) + geom_point() + stat_smooth()
p2 <- ggplot(output, aes(Number_samples, PC2_var)) + geom_point() + stat_smooth()
grid.arrange(p1,p2, nrow=1)
```
<br>`r fig_cap("percentage explained by PCs", "Percentage explained by PC axes according to number of samples analysed")`

@@

```{r, cache = T}
output <- ut(y=exp(ar1), sample_size = c(20:50), threshold_error = c(2:10), each = 100, type="mean")
names(output)
head(output$convergence_cptmean)
ggplot(output$convergence_cptmean, aes(sample_size,number_sample_added)) + geom_point(alpha=.3)

@@

```{r summary }
names(output$random_cptmean)

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = dirname(getwd()))
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

@@

# Libraries
library(dplyr)
require(rioja)
require(vegan)
require(ade4)
require(changepoint)
require(ggplot2)
require(gridExtra)
require(plotly)
library(reshape)

```

@@

```{r strat plot zurich selected sp, echo=FALSE}
if(is.zh){
  par(mfrow=c(1,1))
par(mar=c(5.1,4.1,2.1,20))
clado.clust<-strat.plot(cbind(zh[,colnames(zh) %in% c("LK","SC","DL","EL","EC","BL","BYL")], rowSums(zh[,-1][,!colnames(zh) %in% c("LK","SC","DL","EL","EC","BL","BYL")])),yvar=zh[,1],col.line="black",lwd.line=0,col.bar="black",lwd.bar=2, x.names=c(colnames(zh[colnames(zh) %in% c("LK","SC","DL","EL","EC","BL","BYL")]), "others"), cex.xlabel=1, srt.xlabel=30,scale.minmax=FALSE, y.rev = F,clust=clust)
addClustZone(clado.clust,clust,4,col="black")
}
```
<br>`r fig_cap("strat plot zurich selected sp", "Stratigraphic abundance of dominant cladoceran remains in Lake Zürich sediment core ZH17-21. Abbreviations: BL= Bosmina longirostris, EC= Eubosmina coregoni, EL= Eubosmina longispina, DL= Daphnia spp., LK= Leptodora kindti, BYL= Bythotrephes longismanus, SC= Sida crystallina")`

@@

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=T}
output <- ut(y=exp(ar1), sample_size = c(20:50), threshold_error = c(2:10), each = 100, type="mean")
names(output)
head(output$convergence_cptmean)
ggplot(output$convergence_cptmean, aes(sample_size,number_sample_added)) + geom_point(alpha=.3)

@@

```{r summary, echo=FALSE, message=FALSE, warning=FALSE}
names(output$random_cptmean)

@@

# Do the same but change the location of the changepoint

```{r message=FALSE, warning=FALSE, cache=T, include=FALSE}
shift_vector <- sample(2:99, size = 50, replace = F)

for (i in shift_vector) {
  # Set simulation parameters
mu = 0
sigma = 0.1
phi = 1
shift_time = i
max_time = 100

# Set up vectors
ar1 <- vector(mode = 'numeric',100)
ar1[1] <- 10

# Build time series
for (t in 2:max_time){
  if(t == shift_time){ar1[t-1]=-10}
  ar1[t] <- ar1[t-1] + phi*rnorm(1,mean=mu,sd = sigma)

}

temporary <- ut(y=exp(ar1), sample_size = c(10:50), threshold_error = c(1:10), each = 1, type="mean")

if(i==shift_vector[1]) {
  out_regular_cptmean     <- temporary$regular_cptmean
  out_random_cptmean      <- temporary$random_cptmean
  out_convergence_cptmean <-temporary$convergence_cptmean
} else {
  out_regular_cptmean     <- rbind(out_regular_cptmean, temporary$regular_cptmean)
  out_random_cptmean      <- rbind(out_random_cptmean, temporary$random_cptmean)
  out_convergence_cptmean <- rbind(out_convergence_cptmean, temporary$convergence_cptmean)
}
}

dim(out_regular_cptmean)
dim(out_random_cptmean)
dim(out_convergence_cptmean)

outsumm <- as.data.frame(with(out_random_cptmean, tapply(same_cptmean,list("Initial_number_samples"=sample_size,"threshold_yr"=threshold_error), sum)))
outsumm$InitialNumber <- as.numeric(rownames(outsumm))
outsumm <- melt(outsumm, id.vars = "InitialNumber")
outsumm$more80 <- ifelse(outsumm$value>=50*.8,1,0)

```

```{r}
ggplot(outsumm, aes(InitialNumber, variable, fill=more80)) + geom_tile() +
  xlab("Sample analyzed") + ylab("Tolerance for error (year)")

# Something is wrong here, it is sometimes adding >900 samples.I think it has to do with the while loop in the ut() function.
ggplot(out_convergence_cptmean, aes(sample_size,number_sample_added)) + geom_point(alpha=.3) + ylim(0,25)

boxplot(out_convergence_cptmean$number_sample_added ~ out_convergence_cptmean$sample_size, ylim=c(0,25))
```
